% Abstract

\pdfbookmark[1]{Abstract}{Abstract} % Bookmark name visible in a PDF viewer

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Abstract} % Abstract name

This thesis describes the research conducted on a specific time-aware information extraction task: the prediction of popular activities using Twitter data. The research examines whether popular activities can be accurately predicted and is divided into three subtasks: activity classification, for identification of future activities in messages, activity extraction, for the extraction of activities from messages, and finally a ranking method, used for depicting popularity of an activity. 

The classification of messages in activities is examined for Support Vector Machines (SVM) and Naive Bayes classifiers, conducting experiments with different feature vectors. The SVM classifier using uni- and bigra tokens has the best performance of a 75\% F1-score. 

The extraction of activities is examined using the Latent Dirichlet Allocation (LDA) method and a POS tag approach. The LDA algorithm shows not applicable for the extraction of activities due to sparse data. The POS tag approach shows promising results for the extraction of 66 \% of all activities. 

The ranking of popular activities is conducted using adapted frequency counts. The ranking show promising results in extracting and ranking of the popular activities.

Overall, the three subtasks perform satisfactorily and result in fairly accurate prediction of popular activities. Suggestions for improvements in future work are given regarding the training data and on the extracion of activities.

\endgroup			

\vfill